\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-10 Paper/paper.tex
Something funky is going on... Also added some stuff to defect figure"

>>>>

What we see here is that the earlier a defect is introduced the more it costs to fix it later. Of particular note is that the costs are roughly exponential, not linear. The longer a bug lies undetected, the increasingly harder it becomes to fix that bug. On the flip side, it's relatively easy to fix a bug that was introduced in the same stage that it is found, e.g. introducing a coding bug during ``Construction'' and fixing it while still writing code, prior to the ``System Test'' phase.
